### 2019-06-14 Documents/project_plan/pages/work_plan.tex
Changes; - Updated the plan for the project - Started thinking about an inital pre-pilot question. Added a script to obtain random matches for question material

\subsection*{\hyperref[ref:wordlist]{Wordlist characteristic analysis}}
This area will look into characteristics that are attractive when designing a wordlist. These will be used later to possibility improve the trustword implementation. Past research could provide guidance on this aspect.

\subsection*{Analysis into effective ``similarity'' metrics}
This section will involve research into how similarities in words can be quantified. Which options provide us the best balance of number of matches and accuracy of matches?

\subsection*{Development of a tool used to find partial collisions for wordlist mappings}
This tool would be fed two keys, one ``static'' and one the ``target''. The tool would then generate keys for the ``target'' that create a similar overall wordlist mapping. Here metrics for linguistic distance will be used to define ``similarity''.
The similarity metric will generate a list of keys that provide similar matches, the tool will then hash large number of PGP keys to generate partial matches. This is useful to define an actual measure of the real-world feasibility. This is one aspect missing from the literature as other papers have simulated attacks on encoding schemes.

\subsection*{\hyperref[ref:trustwords]{Security of Trustwords}}
This section will evaluate Trustwords using the previously defined metrics. Alongside this, the feasibility of generating partial collisions will be assessed. The security could be quantified by testing the current implementation out on real users and determining the False Acceptance Rate of near attacks. This could be used as a baseline for improvements to be compared later.

\subsection*{\hyperref[ref:alternatives]{Security of alternative wordlists:}}
In the same way as Trustwords were assessed, the same will be performed on already available wordlists. Such as the PGP wordlist and the wordlist generated by SafeSlinger.

\subsection*{\hyperref[ref:rec]{Security of implemented recommendations}}
This section will then amalgamate all the research performed prior and use it to improve and update the implementation of Trustwords. This would then be assessed by experimentation and the improvements could be quantified with the same experimentation.

% \section{In-depth breakdown}

% \subsection{Wordlist characteristic analysis}
% \label{ref:wordlist}
% \begin{itemize}
%     \item Investigation into characteristics of a strong wordlist
%     \begin{itemize}
%         \item Distinctiveness
%         \item Homonyms (Visual)
%         \item Homophones (Pronunciation)
%         \item Length
%         \item Current ways to define linguistic distance:
%         \begin{itemize}
%             \item \textbf{Visual:}
%             \begin{itemize}
%                 \item Levenshtein (Edit distance)
%             \end{itemize}

%             \item \textbf{Auditory}:
%             \begin{itemize}
%                 \item Soundex
%                 \item Metaphone
%                 \item NYSIIS
%                 \item Match Rating
%             \end{itemize}
%         \end{itemize}

%     \end{itemize}

%     \item Analysis into the strength of the TrustWords using previously obtained metrics.

%     \item Investigation into the strength of other wordlists using defined metrics.
%     \begin{itemize}
%         \item PGP word list
%         \item SafeSlinger
%     \end{itemize}

% \end{itemize}

% \subsection{Security of Trustwords}
% \label{ref:trustwords}
% Here we'd look at the words used in the dictionary and attempt to generate lists of keys that would generate partial collisions these would then be fed into the created tool

% \subsection{Security of alternative wordlists}
% \label{ref:alternatives}

% \subsection{Security of implemented recommendations}
% \label{ref:rec}

>>>>

\subsection{Trustword attacks}

\subsubsection{Similarity metrics}
This section will discuss the feasibility of attacking 4 Trustwords. This will require "similar" words to be detected in the dictionary. Therefore, "similarity metrics" will be required.

Due to the defined use-case of Trustwords to be authenticated over a audio based channel, metrics that measure the pronoucability of a word will be used.

\textbf{[FURTHER WORK: Using metrics that consider the visual aspect of a word - this could be useful due to in-person authentication]}

\begin{itemize}
    \item Soundex
    \item NYSIIS
    \item Match Rating Approach
    \item Word Vectors
    \item Combined (With Levenshtein distance)
\end{itemize}

\textbf{[TODO] Experimentation: } Trimming down these metrics might be required with a quick pilot where I attempt to measure the user-perceived similarity accuracy of the schemes. What could be considered is the number of permutations and the "perceived" similarity.

\subsubsection{Similar list creation}
These metrics then can be used to substitute in place of other words to create a list of near-collision matches/permutations. These will help well generating near-collision keys.

\textbf{CONSIDERATION: } The method works by incrementing the exponent? How does this affect the structure of the key

\subsubsection{Tool design and creation}
Discussion will occur here around the creation of the tool. Will need to talk about the inspiration of the tool (Scallion) and the improvements made over it:
\begin{itemize}
    \item Benchmark of comparison of large number of keys.
    \item Why C++ was used?
\end{itemize}

\subsubsection{Study into the effectiveness of the matches}
The could be with the pilot where the results are extrapolated. There are two ways to run this study:

\begin{itemize}
    \item[1] Actual matches are computed and compared
    \item[2] Evaluation of complexity is computed prior, and for the experiment is simulated.
\end{itemize}

I think actually showing the matches can be actually computed and simulating them in the study gives the best balance. [Option 2]

Would I also want to do this with a random single target key? Or the worst case scenario. There are keys that have a higher number of potential matches, this is due to the words the key's fingerprint is mapped to.

\subsubsection{Conclusion of Trustword security}
This will have a conclusion stating the security of the minimum recommendation of 4 Trustwords.

\textbf{[FURTHER WORK: Evaluation with a higher number of words]}

\subsection{Improvement study}

This 
is recommendations into improvements with Trustwords. This will pretty much revolve around the word vectors and their ability to allow wordlist "strength" to be quantified.

\subsection*{Word vectors}
The strength of the metric was shown in it's own paper with comparison with another famous study into an empirical way to vectorize words. This could even be linked back to the initial pilot study.

\textbf{[FURTHER WORK: More evaluation into the effectiveness of the word vector method]}

\subsection*{Choice of Trustwords}

\begin{itemize}
    \item Homographs (Spelt the same by pronounced differently)
    \item Homonyms   (Different spelling same pronunciation)
\end{itemize}

% https://en.wikipedia.org/wiki/Homograph#/media/File:Homograph_homophone_venn_diagram.png

Here I could make recommendations through improvements on the word lists:

\begin{itemize}
    \item Reduce the size of the wordlist (8bit (256 words)/10bits (1024 words))
    \item Different choice of words
    \item ?
\end{itemize}

These could then be evaluated in a similar way to show possible improvements over the base wordlist used by Trustwords

\textbf{[FURTHER WORK: Other languages found within Trustwords require this evaluation]}
